MSDS 7333 Case Study 06

### 2017-06-20 MSDS7333_CaseStudy06_MBaldree_BBrock_TElkins_AKelly_BBrock-Update.Rmd
add text for weighted K-NN
add text for weighted K-NN

>>>>

In this exercise, we investigated using an alternative k-nearest prediction method using the weighted 
K-nearest neighbors approach.  The calculation of the Euclidean distance error was found to be 1194, whereas the Mean SS error was found to be 210.  The Euclidean distance weighted k-nearest neighbors 
method had the highest error, while the Mean SS weighted K-nearest neighbors method had the smaller
error.

| k |Euclidean distance error|Mean SS error|
|:-:|:-----------------:|:-----------------:|
| |1194|210|
